\Huge ACM and Climate Change

### 2019-05-25 main.tex
Better outline

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\begin{itemize}
\item Reasons in favor:
\begin{itemize}
\item It is the right thing to do: We should be changing our behavior
starting now, and giving ourselves a ``price signal'' is a good way to
achieve this.
\item Offsets reduce carbon emissions now.  (Yes, there are bogus ones, but
not all are bogus.)
\end{itemize}
\item Concerns:
\begin{itemize}
\item 
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\end{itemize}
\item People argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\end{itemize}
\end{itemize}

>>>>

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\end{itemize}
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\item Moreover, offsets are an effective way to reduce carbon emissions {\em
  now}.  (Yes, there are bogus ones, but not all are bogus.)
\item Most importantly, it is the right thing to do: We should be changing
our behavior starting now, and giving ourselves a (correct) ``price signal''
is an effective way to achieve this.
\end{itemize}
